A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-03-17 paper/paper.tex
lics23: write some more responses

\section{Introduction}
In the context of functional programming, Reynolds' parametricity~\cite{reynolds72} interprets types as relations characterizing the observational behavior of programs of this type. Parametricity can be iterated, and it has been noted that iterated Reynolds' parametricity can be interpreted in various various cubical sets~\cite{johann17,altenkirch15,moulin16,moeneclaey21,moeneclaey22phd}. We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates or families instead of relations or graphs, in which case, we obtain a form of realizability~\cite{bernardy12,lasson12,moulin16}. It has then been noted that iterated unary parametricity has an augmented simplicial flavor~\footnote{Private communication with Hugo Moeneclaey and Thorsten Altenkirch}.

>>>>

\section{Introduction}
In the context of functional programming, Reynolds' parametricity~\cite{reynolds72} interprets types as relations characterizing the observational behavior of programs of this type. Parametricity can be iterated, and it has been noted that iterated Reynolds' parametricity can be interpreted in various cubical sets~\cite{johann17,altenkirch15,moulin16,moeneclaey21,moeneclaey22phd}. We obtain a \emph{unary} variant of Reynolds' \emph{binary} parametricity by using predicates or families instead of relations or graphs, in which case, we obtain a form of realizability~\cite{bernardy12,lasson12,moulin16}. It has then been noted that iterated unary parametricity has an augmented simplicial flavor~\footnote{Private communication with Hugo Moeneclaey and Thorsten Altenkirch}.
